---
title: 'RMarkdown:  Day 3 In Class Assignment'
author: "YOUR NAME HERE"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---

```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```

Reminders:

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
  - RStudio’s Markdown Help
  - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well.

# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section below this list named "Your work here". In that section, complete the tasks below:

- Make a *subsection* called Wise Words.
- Put your favorite quote in a block quote.
- Add a working, clickable link to a website that provides more information about that quote.
- Make another *subsection* called "I recommend", and add some information about your favorite author or musician:
  - A *subsubheading* with the name of the artist or author;\
  - An example of their writing or lyrics (formatted in a *block of text*);\
  - A *list* of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.

# Part 2: Code Chunks

Code chunks evaluate code and place the results in the document.

```{r echo=TRUE}
2 + 2
sin(pi)
x <- sample(1:100, 10)
x
mean(x)
```

Complete the following steps here:

- Knit the document and observe what appears in the output.
- Change the chunk option echo=TRUE to echo=FALSE.
- Knit the document again.
- Finally, write 2–3 sentences answering the following questions:
  - What changed between the two outputs?
  - Did the calculation still run when the code was hidden?
  - Why/when might someone want to **hide** code in a report?
  - Why/when might someone want to **show** code in a report?

# Part 3: A small R-in-markdown preview

- Create a subsection within this section called "About this document".
- Write 2–3 sentences describing what this document is and what it produces.
- Include one value generated by inline R code.

> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

# Submitting Instructions

When you are finished:

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file
  - The generated `.html` file
- I'm testing out the autograder in Classroom50, it will check for an html file in the repository.
